---
title: "flat_dev.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# placeholder
    
```{r function-placeholder}
#' placeholder
#' 
#' creat a dir that is not empty
#' @param path char,a dir to be make
#' @return path
#' 
#' @export
placeholder <- function(path){
    fs::dir_create(path = path)
  writeLines("",con = paste0(path,"/place.holder"))
  return(path)
}
```
  
```{r example-placeholder}
placeholder("testtemp")
fs::dir_delete("testtemp")
```
  
```{r tests-placeholder}
test_that("placeholder works", {
  expect_true(inherits(placeholder, "function")) 
})
```
  
# docker_install
    
```{r function-docker_install}
#' docker_install
#' 
#' install docker in linux systems
#' @param system linux,macos,windows
#' @return null
#' 
#' @export
docker_install <- function(system){
  if (system == "linux"){
    message("Note,install docker for linux servers")
  system("sudo wget -qO- https://github.com/rainoffallingstar/beaverdown/blob/main/dev/docker_install.sh | bash
")
  }else if(system == "macos"){
    system("brew install docker docker-compose")
  }else{
    system("winget install Docker.DockerDesktop")
  }
  
}
```
  
```{r example-docker_install}

```
  
```{r tests-docker_install}
test_that("docker_install works", {
  expect_true(inherits(docker_install, "function")) 
})
```
  
# minikube_install
    
```{r function-minikube_install}
#' minikube_install
#' 
#' install minikube
#' @param system linux,macos,windows
#' @return null
#' 
#' @export
minikube_install <- function(system = c("linux","macos","windows")){
  if (system == "linux"){
    message("Note,install minikube for linux servers")
  system("sudo wget -qO- https://github.com/rainoffallingstar/beaverdown/blob/main/dev/minikube_install.sh | bash
")
  }else if (system == "macos"){
  system("brew install minikube")
  } else {
  system("winget install Kubernetes.minikube")
}
  
}
```
  
```{r example-minikube_install}

```
  
```{r tests-minikube_install}
test_that("minikube_install works", {
  expect_true(inherits(minikube_install, "function")) 
})
```
  
# minikube_start
    
```{r function-minikube_start}
#' minikube_start
#' 
#' start a cluster by minikube
#' 
#' @return null
#' 
#' @export
minikube_start <- function(){
    system("minikube start")
}
```
  
```{r example-minikube_start}

```
  
```{r tests-minikube_start}
test_that("minikube_start works", {
  expect_true(inherits(minikube_start, "function")) 
})
```
  
# kubectl_install
    
```{r function-kubectl_install}
#' kubectl_install
#' 
#' install kubectl in linux
#' @param system linux,macos,windows
#' @return null
#' 
#' @export
kubectl_install <- function(system = c("linux","macos","windows")){
  if (system == "linux"){
    system("curl -LO 'https://dl.k8s.io/release/$(curl -L -s https://dl.k8s.io/release/stable.txt)/bin/linux/amd64/kubectl'  && sudo install -o root -g root -m 0755 kubectl /usr/local/bin/kubectl ")
  } else if (system == "macos"){
    system("brew install kubectl
")
  } else if (system == "windows"){
    system("winget install Kubernetes.kubectl")
  }
    
}
```
  
```{r example-kubectl_install}

```
  
```{r tests-kubectl_install}
test_that("kubectl_install works", {
  expect_true(inherits(kubectl_install, "function")) 
})
```
  
# kubectl_apply
    
```{r function-kubectl_apply}
#' kubectl_apply
#' 
#' kubectl_apply functions
#' @param yamlfiles chr
#' @param namespace chr,default as NULL
#' @return yamlfiles
#' 
#' @export
kubectl_apply <- function(yamlfiles,namespace = NULL){
    if (!file.exists(yamlfiles)) stop("the yamlfiles not found")
  command = glue::glue("kubectl apply -f {yamlfiles}")
  if (!is.null(namespace)) command = glue::glue("{command} -n {namespace}")
  message(glue::glue("RUN for {command}"))
  system(command)
  return(yamlfiles)
}
```
  
```{r example-kubectl_apply}

```
  
```{r tests-kubectl_apply}
test_that("kubectl_apply works", {
  expect_true(inherits(kubectl_apply, "function")) 
})
```
  
# kubectl_get
    
```{r function-kubectl_get}
#' kubectl_get
#' 
#' kubectl_get functions for 
#'  deployments,service,ingress,namespaces,configmap,jobs,
#'  cronjob,secret,endpoints
#' @param servicetype chr,one of the following:deployments,service,ingress,namespaces,configmap,jobs, cronjob,secret,endpoints
#' @return data.frame
#' 
#' @export
kubectl_get <- function(servicetype){
  if (servicetype %in% c('deployments','service','ingress','namespaces','configmap','jobs', 'cronjob','secret','endpoints')){
    command <- glue::glue("kubectl get {servicetype}")
    if (servicetype == "configmap") command = paste(command,"--all-namespaces")
    message(glue::glue("RUN for {command}"))
  data <- system(command,intern = T) %>%
    {
  output <- .
  header <- output[1]
  data_lines <- output[-1]
  data <- do.call(rbind, lapply(data_lines, function(x) {
    strsplit(x, "\\s{2,}")[[1]]
  }))
  header_clean <- strsplit(header, "\\s{2,}")[[1]]
  if (ncol(data) == length(header_clean)) {
    colnames(data) <- header_clean
    data <- as.data.frame(data)
  }
    }
  return(data)
  }else {
    stop("choose the right function to be get inside one of the following:deployments,service,ingress,namespaces,configmap,jobs, cronjob,secret,endpoints")
  }
    
}
```
  
```{r example-kubectl_get}

```
  
```{r tests-kubectl_get}
test_that("kubectl_get works", {
  expect_true(inherits(kubectl_get, "function")) 
})
```
  
# kubectl_portforward
    
```{r function-kubectl_portforward}
#' kubectl_portforward
#' 
#' kubectl port-forward warpper
#' @param podname the podname
#' @param hostport the hostport
#' @param childport the childport for the containers
#' @return NULL
#' 
#' @export
kubectl_portforward <- function(podname,
                                hostport,
                                childport){
    command = glue::glue("kubectl port-forward {podname} {hostport}:{childport}")
    message(glue::glue("RUN for {command}"))
  system(command)
  return(podname)
}
```
  
```{r example-kubectl_portforward}

```
  
```{r tests-kubectl_portforward}
test_that("kubectl_portforward works", {
  expect_true(inherits(kubectl_portforward, "function")) 
})
```
  
# kubectl_exec
    
```{r function-kubectl_exec}
#' kubectl_exec
#' 
#' kubectl exec wrapper 
#' @param podname podnames
#' @param arg_command the command to be ran
#' @return NULL
#' 
#' @export
kubectl_exec <- function(podname,
                         arg_command){
    command <- glue::glue("kubectl exec -it {podname} /bin/bash {arg_command} ")
    message(glue::glue("RUN for {command}"))
  system(command)
  return(podname)
}
```
  
```{r example-kubectl_exec}

```
  
```{r tests-kubectl_exec}
test_that("kubectl_exec works", {
  expect_true(inherits(kubectl_exec, "function")) 
})
```
  
# kubectl_logs
    
```{r function-kubectl_logs}
#' kubectl_logs
#' 
#' kubectl logs wrapper 
#' @param podname the podname
#' @return NULL
#' 
#' @export
kubectl_logs <- function(podname){
    command <- glue::glue("kubectl logs --follow {podname}")
    message(glue::glue("RUN for {command}"))
  system(command)
  return(podname)
}
```
  
```{r example-kubectl_logs}

```
  
```{r tests-kubectl_logs}
test_that("kubectl_logs works", {
  expect_true(inherits(kubectl_logs, "function")) 
})
```
  
# kubectl_delete
    
```{r function-kubectl_delete}
#' kubectl_delete
#' 
#' kubectl delete warpper
#' 
#' @param servicetype chr,one of the following:deployments,service,ingress,namespaces,configmap,jobs, cronjob,secret,endpoints
#' @param object the object to remove
#' @return chr
#' 
#' @export
kubectl_delete <- function(object,servicetype){
    if (grep(".yaml",object)){
      if (!file.exists(object)) stop("the yamlfile not found")
      command <- glue::glue("kubectl delete -f {object}")
    } else {
      if (!(servicetype %in% c('deployments','service','ingress','namespaces','configmap','jobs', 'cronjob','secret','endpoints'))) stop("choose the right function to be get inside one of the following:deployments,service,ingress,namespaces,configmap,jobs, cronjob,secret,endpoints")
      command <- glue::glue("kubectl delete {servicetype} {object}")
    }
  message(glue::glue("RUN for {command}"))
  system(command)
  return(object)
}
```
  
```{r example-kubectl_delete}

```
  
```{r tests-kubectl_delete}
test_that("kubectl_delete works", {
  expect_true(inherits(kubectl_delete, "function")) 
})
```
  
# submit_job
    
```{r function-submit_job}
#' submit_job
#' 
#' submit_job and run
#' @param task_names the name of the submit job
#' @param namespace the namespace used 
#' @param container the container used
#' @param command the command submit to run
#' @param ncpu the cpu request
#' @param nram the memory request
#' @param cpu_limit the limit cpu
#' @param nram_limit the nram limit
#' @param env_list the env value list,default as NULL
#' @param restartPolicy the restartPolicy,default as Never
#' @param hostPath the attached hostpath,default as the current file dir,attached to /mnt in the container
#' @return NULL
#' 
#' @export
submit_job <- function(task_names,
                       namespace = "default",
                       container,
                       command,
                       ncpu = 8,
                       nram = "1024Mi",
                       cpu_limit = 100,
                       nram_limit = "10240000Mi",
                       env_list = NULL,
                       hostPath = getwd(),
                       restartPolicy = "Never"){
    job_yaml = job_yaml
    # namespace 
    job_yaml$metadata$namespace <- namespace
    # task_names
    job_yaml$metadata$name <- task_names
    job_yaml$metadata$labels$app <- task_names
    job_yaml$spec$template$metadata$name <- task_names
    job_yaml$spec$template$metadata$labels$app <- task_names
    job_yaml$spec$template$spec$containers[[1]]$name <- task_names
    # containers
    job_yaml$spec$template$spec$containers[[1]]$image <- container 
    # command 
    job_yaml$spec$template$spec$containers[[1]]$command <- stringr::str_replace(job_yaml$spec$template$spec$containers[[1]]$command,"command",command)
    # resources_request
    # cpu
    job_yaml$spec$template$spec$containers[[1]]$resources$requests$cpu <- ncpu
    #memory
    job_yaml$spec$template$spec$containers[[1]]$resources$requests$memory <- nram
    # resources_limit 
    # cpu
    job_yaml$spec$template$spec$containers[[1]]$resources$limits$cpu <- cpu_limit
    #memory
    job_yaml$spec$template$spec$containers[[1]]$resources$limits$memory <- nram_limit
    # env
    if (!is.null(env_list))job_yaml$spec$template$spec$containers[[1]]$env <- env_list
    #job_yaml$spec$template$spec$volumes[[1]]$hostPath <- "C/zoneinfo/Asia/Shanghai"
    #volumes(current dir)
    job_yaml$spec$template$spec$volumes[[2]]$hostPath <- as.character(hostPath) %>% 
      stringr::str_remove(.,":")
    # restart #job_yaml$spec$template$spec$dnsPolicy
    job_yaml$spec$template$spec$restartPolicy <- restartPolicy
    fs::dir_create(paste0(
      hostPath,"/result/yaml/"
    ))
    yamlfile <- paste0("result/yaml/",task_names,".yaml")
    yaml::write_yaml(job_yaml,file = yamlfile )
    message("runs the yamlfile")
    kubectl_apply(yamlfiles = yamlfile,
                  namespace = namespace)
    return(task_names)
}
```
  
```{r example-submit_job}

```
  
```{r tests-submit_job}
test_that("submit_job works", {
  expect_true(inherits(submit_job, "function")) 
})
```
  
# act_install
    
```{r function-act_install}
#' act_install
#' 
#' install act and run github action locally
#' @param system chr
#' @return NULL
#' 
#' @export
act_install <- function(system = c("linux","macos","windows")){
    if (system == "macos"){
      system("brew install act")
    }else if (system == "windows"){
      system("winget install nektos.act")
    }else{
      system("curl --proto '=https' --tlsv1.2 -sSf https://raw.githubusercontent.com/nektos/act/master/install.sh | sudo bash")
    }
}
```
  
```{r example-act_install}

```
  
```{r tests-act_install}
test_that("act_install works", {
  expect_true(inherits(act_install, "function")) 
})
```
  

# act_local
    
```{r function-act_local}
#' act_local
#' 
#' act_local
#' @param yamlfile workflow files
#' @param arg args
#' @return yamlfile
#' 
#' @export
act_local <- function(yamlfile,arg = NULL){
  
  if (!file.exists(yamlfile)){
    stop("workflow file not found")
  }
  command <- glue::glue("act -W {yamlfile}")
  if (!is.null(arg)){
    command <- glue::glue("{command} {arg}")
  }
  
  system(command = command)
  return(yamlfile)
    
}
```
  
```{r example-act_local}

```
  
```{r tests-act_local}
test_that("act_local works", {
  expect_true(inherits(act_local, "function")) 
})
```
  
<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_dev.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
